Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-17 report/report.tex
Add figure comparing footpaths and residential streets

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_map_residential_footpath_compare}
    \caption{Example segments of the Stockholm metropolitan area with highlighted residential streets (left) and footpaths (right). Here can be seen the unique character of footpaths. Walkways in parks appear to grow much more organically, and pavements form rough grid systems with organic branches that bridge over city blocks.}
    \label{fig:osm-slu-map}
\end{figure}
